%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
%\let\nofiles\relax
\documentclass{my_cv} 

\usepackage{hyperref}
\usepackage[letterpaper,bindingoffset=0.2in,left=0.75in,right=0.75in,top=0.5in,bottom=1in,footskip=0.4in]{geometry}

\usepackage{marvosym}
\usepackage{fontawesome}
\usepackage{academicons}
\usepackage[document]{ragged2e}

\usepackage[backend=bibtex,
style=numeric,
style=alphabetic,
bibencoding=ascii,
defernumbers=true,
style=ieee,
sorting=nyt
]{biblatex}
\addbibresource{cv_1}
\nocite{*}



\usepackage{xcolor}
 \definecolor{linkedincolor}{HTML}{1683BB}
\definecolor{facebookcolor}{HTML}{3b5998 }
\definecolor{gscholarcolor}{HTML}{6699FF }

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------
\setlength{\parindent}{0pt}
\begin{document}

\name{\textsc{Venkaiah Chowdary Kavuri}}
\vspace{-2mm}
\begin{center} 
\begin{footnotesize}
\contact{4404 Walnut St., \# 3R}{Philadelphia, PA}{USA 19104}{\faEnvelope\,  \href{mailto:venk@sas.upenn.edu}{venk@sas.upenn.edu}}{\faMobilePhone\, (814) 431-2033}
\end{footnotesize}

\href{https://www.linkedin.com/in/venkaiahchowdarykavuri}{\textcolor{linkedincolor}{\faLinkedinSquare}} \href{https://github.com/Venki-Kavuri}{\faGithub} \href{https://scholar.google.com/citations?hl=en&user=r5E9ACIAAAAJ&view_op=list_works}{\textcolor{gscholarcolor}{\aiGoogleScholar}} \href{https://www.facebook.com/venki.kavuri}{\textcolor{facebookcolor}{\faFacebookOfficial}}
\end{center} 
%----------------------------------------------------------------------------------------

\vspace{-9mm} 

\section{Summary of Qualifications}
\begin{itemize}\itemsep 0pt

\item Optical device instrumentation and characterization - Lasers, Optoelectronics and CCD cameras. 
\item Deep understanding of the fundamental physics of light-optical modeling/simulation/optimization.
\item Instrument control and data processing- LabVIEW, MATLAB, Python, and SOLIDWORKS. 
\item Statistics- Design of Experiments, SAS and SPSS.
\item Electronic circuit design- PSpice.
\item Signal processing tools- Short time Fourier transform, Wavelet transform, Noise filtering and Parameter estimation.
\end{itemize}
\vspace{-7mm}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\begin{flushleft}  
\textbf{University of Pennsylvania}, Philadelphia, PA  \hfill October 2014 - Present \\ 
Postdoctoral Researcher in Department of Physics and Astronomy \\ 
\vspace{-2.5mm}
\begin{itemize}\itemsep -2pt
\item Projects in progress: Time-domain and Frequency-domain(100MHz) Optical instrumentation (stroke measurements) for Neural ICU.   
\item Completed projects: Optical 3D image reconstruction (inverse problem) of human breast cancer from 2D camera images. 
\item Advisor: Professor Arjun Yodh
\item Areas of focus: Optical Instrument Design, Clinical Measurements, Diffuse Optical Tomography, Diffuse Coherence Spectroscopy and Image Reconstruction.
\end{itemize}


\textbf{University of Texas Arlington}, Arlington, TX \hfill January 2008 - August 2014 \\ 
Doctor of Philosophy in Biomedical Engineering (Medical Imaging-Biomedical Optics) \\
\vspace{-2.5mm}
\begin{itemize}\itemsep -2pt
\item Dissertation -  Development of Trans-rectal Ultrasound (TRUS) Coupled Diffuse Optical Tomography (DOT) For Prostate Cancer Imaging.
\item Advisor: Professor Hanli Liu 
\item Areas of focus: Optical Probe Design, Clinical Measurements, Image Reconstruction and Image Processing.
\end{itemize}
 
\textbf{Jawaharlal Nehru Technological University}, Hyderabad, India \hfill September 2003 - May 2007\\
Bachelor of Technology in Biomedical Engineering \\ 
\vspace{-3mm}
\begin{itemize}
\setlength\itemsep{0em} 
\item First class with distinction.
\end{itemize}
\end{flushleft}  
%----------------------------------------------------------------------------------------
 
\vspace{-7mm}% Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}
\begin{flushleft}  

\textbf{University of Pennsylvania}, Philadelphia, PA . \hfill October 2014 - Present \\ 
\textbf{\textcolor{darkgray}{Postdoctoral Researcher,} }Yodh Biomedical Optics Lab, Philadelphia, PA
\vspace{-2.5mm}
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Designed a non-invasive cerebral blood flow instrument to be used in neural ICU for predicting recurrent stroke using single photon counting detectors and long coherence length lasers. 
\item Image processing and reconstruction of breast cancer images (using diode lasers and gain modulated, image intensified CCD camera) using Diffuse Optical Tomography (optical 3D mammogram).
\item Supervised and trained new graduate students, undergraduate students and research assistants.  
\end{itemize}

\textbf{University of Texas Arlington}, Arlington, TX \hfill August 2010 - August 2014 \\
\textbf{\textcolor{darkgray}{Graduate Research Assistant,} }Biomedical Optics Lab, Arlington, TX 
\begin{itemize} \itemsep -2pt % Reduce space between items
\vspace{-2.5mm}
\item Developed a technique to detect and image early stages of aggressive prostate cancer by creating, engineering and building Trans-rectal Ultrasound (TRUS)-compatible Diffuse Optical Tomography (DOT) Probe (using SolidWorks), which increased sensitivity and specificity to detect prostate cancer. 

\item Originated, designed and built multi-spectral, low-cost and portable DOT instrumentation (using basic electronic circuit design and signal processing) then improved existing reconstruction methods (enhanced depth localization and images) by combining depth compensation algorithm and L1-regularized least squares method.

\item Research work resulted in 2 peer-reviewed, 1st-authored journal papers. This produced further external funding for continuous development in detection/diagnosis of prostate cancer.

\end{itemize}
\end{flushleft}
 
%----------------------------------------------------------------------------------------

\vspace{-7mm} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Computer Skills}

\vspace{2pt} % Gap between title and text
\begin{center}

\begin{tabular}{c|c|c|c|c|c} Matlab & LabVIEW& Python & C &SOLIDWORKS &Comsol \\
MS Office& Ubuntu & ImageJ &\LaTeX &SAS &SPSS\end{tabular}
\end{center}


\vspace{-7mm}  % Some whitespace between sections
%----------------------------------------------------------------------------------------
%	EQUIPMENT SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Equipment Skills}

\vspace{2pt} % Gap between title and text
\begin{center}

\begin{tabular}{c|c|c|c|c} Oscilloscopes & Spectrum Analyzers & RF Electronics (100-200MHz) & Lock-in Amplifiers &Spectrometers\\
Lasers \& LEDs & Optoelectronics &Photon Counting &DAQ boards &Free Space Optics\end{tabular}
\end{center}

%----------------------------------------------------------------------------------------

\vspace{-7mm}  % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PATENTS SECTION
%----------------------------------------------------------------------------------------

\section{{Patents}} 

\vspace{-2mm} % Gap between title and text
\begin{itemize} \itemsep -2pt % Reduce space between items
\item ``TRUS-Integrated FD-DOI Multi-modal Imaging System for Prostate Cancer," US Provisional Patent Application Serial No. 61/985,905, April 2014. 
\end{itemize}


%----------------------------------------------------------------------------------------

\vspace{-5mm} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

\section{{Memberships}} 

\vspace{-2mm} % Reduce space between section title and contents

\begin{itemize} \itemsep -2pt 
\item Member, International Professional Society for Optics and Photonics Technology(SPIE).
\item Member, Optical Society of America(OSA). 
\item Member, Institute of Electrical and Electronics Engineers(IEEE). 
\end{itemize}

%-------------------------------------of---------------------------------------------------

\vspace{-5mm} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\section{{Honors}} 

\vspace{-5pt} % Reduce space between section title and contents
\begin{itemize} \itemsep -2pt 
\item STEM Full tuition assistantship, University of Texas Arlington. \\
\item Outstanding Student Award - 2014, University of Texas Arlington. \\
\end{itemize}
%----------------------------------------------------------------------------------------

\vspace{-7mm}  % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{{Publications}} 
\vspace{-5pt} 
\printbibliography[title={Articles},type=article,heading=subbibliography]
\vspace{-6mm}
\printbibliography[title={Conference Publications},type=inproceedings,heading=subbibliography]

%----------------------------------------------------------------------------------------

\let\thefootnote\relax\footnotetext{Resume compiled on \today}
\end{document}
